% LaTeX file for resume 
% This file uses the resume document style (res.sty)

\documentstyle[margin]{res} 
\textwidth=5.6in % increase textwidth to get
		 % smaller right margin
%  Use \documentstyle[margin,newcent]{res} to get New Century Schoolbook 
%                                                         postscript font  
% and \documentstyle[margin]{res} for default (Computer Modern) font
% the margin option causes section titles to appear to the left of
% the body text 

\begin{document} 
 
\name{Benjamin James Anhalt\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{945 Tennessee St \\ Lawrence, KS 66044 \\
        (785) 393-1858 \\ ben.anhalt@gmail.com}

 
\begin{resume}  

\section{Skills}
\underline{Full--stack Web Development}\\
\begin{quote}
\begin{itemize}
\item Expert Python developer. Emphasis on Django, SQLAlchemy.
\item Expert Javascript developer. Emphasis on Backbone.js, JQuery,
  Webpack.
\item Expert in SQL. Emphasis on MySQL. Prefer PostgreSQL.
\item Advanced in Apache httpd configuration. Familiar with Nginx. 
\item Intermediate skill with HTML and CSS.
\item Intermediate skill in Elm.
\end{itemize}
\end{quote}

\underline{Java Development}\\
\begin{quote}
\begin{itemize}
\item Advanced Java developer.
\item Intermediate skill with Maven.
\item Intermediate skill with Ant.
\end{itemize}
\end{quote}

\underline{DevOps}\\
\begin{quote}
\begin{itemize}
\item Advanced skill with Git and GitHub.
\item Experience with DigitalOcean hosting.
\item Experience with Travis CI.
\end{itemize}
\end{quote}

\underline{Linux}\\
\begin{quote}
\begin{itemize}
\item Advanced understanding of Ubuntu systems.
\item Advanced skill with Unix utilities.
\item Intermediate skill with networking.
\end{itemize}
\end{quote}


\section{Experience}
\underline{University of Kansas -- Biodiversity Institute}, Lawrence, KS\\
\begin{quote}
\emph{Research Engineer}, 2014 - Present
\begin{quote}
Team member on the Specify biological collection data management
software project. Lead developer on the Specify 7 web application
including new SaaS offering, new feature development and
maintenance. Contributing developer on Specify 6 maintenance
tasks. Duties also include dev--ops role: build automation, toolchain
management and deployment. Team member on Lifemapper data modeling and
analysis project focusing on front--end web development.
\end{quote}

\emph{Programmer I}, 2011 - 2014
\begin{quote}
Team member on the Specify project. Implemented new features and
contributed to maintenance of the Specify 6 software package. Led
development of the novel Specify 7 web based system including
technology selection, architecture, planning and implementation.
\end{quote}
\end{quote}

\underline{Leia Lulu Properties}, Lawrence, KS\\
\begin{quote}
\emph{Software Engineer}, 2006 - 2011
\begin{quote}
Developed industry -- first managment solution for successful virtual world 
real estate business. Features include transaction processing, notification 
and scheduling, data tracking and mapping services.
\end{quote}
\end{quote}

\underline{University of Kansas -- Dept. of Physics and Astronomy},
Lawrence, KS\\

\begin{quote}
\emph{Research Assistant},  2003 - 2006
\begin{quote}
Studied nonlinear beam -- beam effects in the Tevatron.  Activities
included development of simulation code in C with use of legacy
FORTRAN code and libraries.
\end{quote}

\emph{Teaching Assistant},  2002 - 2003
\begin{quote}
Taught three sections of physics lab over two semesters for the first
calculus based physics course for physics majors.
\end{quote}
\end{quote}

\section{Education} 

\underline{University of Kansas}, Lawrence, KS, 2002 - 2006\\

\begin{quote}
\emph{Master of Science}, Physics, 2006 
\end{quote}

\underline{Missouri State University}, Springfield, MO, 1996 - 2001\\

\begin{quote}
\emph{Bachelor of Science}, 2000 
\begin{quote}
Magna Cum Laude in the Honors College\\
Major: Physics\\ 
Minor: Mathematics\\ 
\end{quote}
\end{quote}


\end{resume}
\end{document}
